---
title: "IE 522 HW12"
author: "Sufan Wang"
date: "2020/11/29"
output:
  word_document: default
  pdf_document: default
---

Consider the simple linear regression model $Y=\beta_1+\beta_2X+\epsilon$, where $\epsilon\sim N(0,\sigma^2)$. There are two sets of data of the same size $n=500$ from this model: $\{(X_{1i},Y_{1i}),1\le i\le n\}$ and $\{(X_{2i},Y_{2i}),1\le i\le n\}$. 

1. (1 point) According to the following scatter plots, which data set will give a more precise estimate for $\beta_2$? Why? 
  
X2 will give a more precise estimate for β2, because the data of X2 are more dispersive, which will result in larger $\sqrt{Sxx}$, and smaller standard error of $\beta$.



2. (1 point) The sample mean and sample variance of $\{X_{1i},1\le i\le n\}$ are 4.98 and 0.10, respectively. The sample mean and sample variance of $\{X_{2i},1\le i\le n\}$ are 4.90 and 2.73, respectively. Which data set will give a more precise estimate for $\beta_1$? Why? 

(4.98^2)/(0.1*499)=0.497002
(4.9^2)/(2.73*499)=0.01762499
X2 will give a more precise estimate for $\beta_1$,because estimated standard error of $\beta_1$ is $\sigma\sqrt{\frac{1}n+\frac{\bar{X}_n^2}{Sxx}}$.




In the following, $\{(X_{2i},Y_{2i}),1\le i\le n\}$ is used to fit the simple linear regression model.

3. (1 point) The sample variance of $\{Y_{2i},1\le i\le n\}$ is $3.56$. What's the total sum of squares? 
SST=3.56*499=1776.44
The total sum of squares is 1776.44.




4. (1 point) The residual standard error is $0.997$. What's the corresponding error sum of squares?
 
SSE=0.997^2*498= 495.016482
The corresponding error sum of squares is 495.016482.



5. (1 point) What's the regression sum of squares? 

SSR=SST-SSE=1281.423518
The regression sum of squares is 1281.423518


  
6. (1 point) What's $R^2$? What's the sample correlation coefficient between $\{X_{2i},1\le i\le n\}$ and $\{Y_{2i},1\le i\le n\}$? 

$R^2$=SSR/SST=1281.423518/1776.44=0.7213435
$R^2$ is 0.7213435.

rho = $\sqrt{R^2}$= 0.8493195
The sample correlation coefficient between $\{X_{2i},1\le i\le n\}$ and $\{Y_{2i},1\le i\le n\}$ is 0.8493195.



7. (1 point) The sample mean of $\{Y_{2i},1\le i\le n\}$ is $14.9$. What are $\hat{\beta}_1$ and $\hat{\beta}_2$? 

Sxx = 2.73*499
$\hat{\beta}_2$ = $\sqrt{SST/Sxx*R^2}$=0.9698727
$\hat{\beta}_1$ = 14.9 -$\hat{\beta}_2$*4.9=10.14762



  
8. (1 point) What's the 95% confidence interval for $\beta_2$? At a significance level of $\alpha=5\%$, is there strong enough evidence that $\beta_2\neq 0$?
```{r}
beta_2_hat=0.9698727
beta_1_hat=10.14762
S_xx=2.73*499
lb=beta_2_hat-qt(0.975,498)*0.997/sqrt(S_xx)
ub = beta_2_hat+qt(0.975,498)*0.997/sqrt(S_xx)
lb
ub
```

The 95% confidence interval for $\beta_2$ is [0.9168003,1.022945],there is not strong enough evidence that $\beta_2\neq 0$.

  
9. (1 point) What's the p-value of the F-test for testing $H_0: \beta_2=0; H_1: \beta_2\neq 0$? 
```{r}
SSE=495.016482
SSR=1281.423518
pf(SSR*498/SSE,1,498, lower.tail = FALSE)
```




10. (1 point) For a new observation $X^*=1$, compute the predicted value $\hat{Y}^*$. Construct a 95% prediction interval for the true value $Y^*$.  

```{r}
m=beta_1_hat+beta_2_hat*1
m

```
The predicted value $\hat{Y}^*$ is 11.11749.
```{r}
ub2 = m + qt(0.975,498)*0.997*sqrt(1+1/500+(4.9-1)^2/S_xx)
lb2 = m - qt(0.975,498)*0.997*sqrt(1+1/500+(4.9-1)^2/S_xx)
ub2
lb2
```  

95% prediction interval for the true value $Y^*$ is[9.145796,13.08919].
