---
title: "IE 522 HW09"
author: "null"
date: "null"
output:
  word_document: default
  pdf_document: default
---


In the following, $\{\epsilon_t\}$ is a white noise with variance $\sigma^2_\epsilon$. 

For problems 1-4, consider a MA(3) process $Y_t=\mu+\epsilon_t+\theta_1\epsilon_{t-1}+\theta_2\epsilon_{t-2}+\theta_3\epsilon_{t-3}$. 

1. (1 point) For what $\theta_1, \theta_2, \theta_3$, is ${Y_t}$ stationary (here stationarity refers to weak stationarity)?





2. (1 point) What's the variance of $Y_t$?




    
3. (1 point) What's the lag-1 autocorrelation? 





4. (1 point) What's the lag-4 autocorrelation? 





5. (1 point) For the following dataset, plot the acf. 
\scriptsize
    ```{r}
    x=read.table("https://faculty.chicagobooth.edu/-/media/faculty/ruey-s-tsay/teaching/fts3/m-ibm3dx2608.txt",header=TRUE)
    r=x$vwrtn
    ```
\normalsize

```{r}
x=read.table("https://faculty.chicagobooth.edu/-/media/faculty/ruey-s-tsay/teaching/fts3/m-ibm3dx2608.txt",header=TRUE)
r=x$vwrtn
plot(acf(r))
```



6. (1 point) Fit MA models up to order 5 to the above dataset. Which MA model fits the data the best? Report the corresponding parameters of the model. 
```{r}
arima(r,order=c(0,0,1))
arima(r,order=c(0,0,2))
arima(r,order=c(0,0,3))
arima(r,order=c(0,0,4))
arima(r,order=c(0,0,5))
```
MA(5) fits the data the best.
$\theta_1=0.1201, \theta_2=0.0022, \theta_3=-0.1169,\theta_4=-0.0120,\theta_5=0.0797,\mu= 0.0089$


7. (1 point) Let $\phi(L)=1+\frac{1}{2}L$. What's $\phi(L)^{-1}$?

$\phi(L)^{-1}=1-\frac{1}{2}L+\frac{1}{4}L^{2}-...$



8. (1 point) Is $\phi(L)^{-1}$ absolutely summable? Is $\phi(L)^{-1}\epsilon_t$ stationary? 

$\phi(L)^{-1}$ is absolutely summable because $\mid\phi1\mid=\frac{1}{2}<1$.
$\phi(L)^{-1}\epsilon_t$ is stationary because $\epsilon_t$ is stationary.



9. (1 point) Consider an AR(1) process $Y_t=3-\frac{1}{2}Y_{t-1}+\epsilon_t$. Is $\{Y_t\}$ stationary? What's the mean of $Y_t$?





10. (1 point) Provide the MA($\infty$) representation for $Y_t$ in question 9. 




